MCC model predictions overview

### 2018-05-18 stats/ex3_comparisons.Rmd
overview model comparisons

@@

llh.plot <- likelihood_overview %>%
  group_by(Model)%>%
  summarize(logSumExp = logSumExp(value))%>%
  mutate(Model = reorder(Model,logSumExp))

>>>>

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

@@

llh.plot <- likelihood_overview %>%
  group_by(Model)%>%
  summarize(logSumExp = logSumExp(value),
            max = max(value))%>%
  mutate(Model = reorder(Model,logSumExp))

### 2018-05-18 stats/summary_model_predictions.Rmd
overview model comparisons

```{r, include = FALSE}
a <- ggplot(p.com, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Adjustment*Type, labeller = label_wrap_gen(width=5))+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)+
  theme(legend.position="bottom")
```

@@

## Correlations between mocel predictions and data

```{r, include = FALSE}
b <-ggplot(data = plot.model,aes(x = mean, y = Data, col = Model)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  facet_grid(Type~Adjustment)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()
```

@@

## Prior only Model with Noise
Mean noise parameter with 95% Credible Interval: `r round(mean(posterior.noise1$value),2)` [`r round(hdi_lower(posterior.noise1$value),2)` : `r round(hdi_upper(posterior.noise1$value),2)`].

@@

Qualitatively, predictions change for different speaker - congruent (from above chance to chance).

## RSA Model with Noise
Noise parameter: `r round(mean(posterior.noise$value),2)` [`r round(hdi_lower(posterior.noise$value),2)` : `r round(hdi_upper(posterior.noise$value),2)`]

@@

## Prior only Model with regularized Priors
Prior Exponent: `r round(mean(posterior.noise3$value),2)` [`r round(hdi_lower(posterior.noise3$value),2)` : `r round(hdi_upper(posterior.noise3$value),2)`].

@@

Qualitatively, predictions change again for different speaker - congruent (from above chance to below chance).

## RSA Model with regularized Priors
Prior Exponent: `r round(mean(posterior.noise2$value),2)` [`r round(hdi_lower(posterior.noise2$value),2)` : `r round(hdi_upper(posterior.noise2$value),2)`]

@@

## Prior only Model with Noise and regularized Priors
Noise parameter: `r round(mean(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)`].

@@

## RSA Model with Noise and regularized Priors
Mean noise parameter with 95% CrI: `r round(mean(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)`].

@@

## Comparing models
```{r model predictions log likelihood, include = FALSE}
c <- ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
llh.plot%>%
  knitr::kable(digits = 3)
```

@@

>>>>

```{r, include = FALSE}
a <- ggplot(p.com, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Adjustment*Type, labeller = label_wrap_gen(width=5))+
  theme_few(base_size = 8) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)+
  theme(legend.position="bottom")
```

@@

## Correlations between model predictions and data

```{r, include = FALSE}
b <-ggplot(data = plot.model,aes(x = mean, y = Data, col = Model)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  facet_grid(Type~Adjustment)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  stat_cor(method = "pearson", label.x = 0.3, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()
```

@@

## Model descriptions

### Prior only Model with Noise
Mean noise parameter with 95% Credible Interval: `r round(mean(posterior.noise1$value),2)` [`r round(hdi_lower(posterior.noise1$value),2)` : `r round(hdi_upper(posterior.noise1$value),2)`].

@@

Qualitatively, predictions change compared to no adjustment predictions for different speaker - congruent (from above chance to chance).

4/8 predictions are qualitatively correct.

### RSA Model with Noise
Noise parameter: `r round(mean(posterior.noise$value),2)` [`r round(hdi_lower(posterior.noise$value),2)` : `r round(hdi_upper(posterior.noise$value),2)`]

@@

8/8 predictions are qualitatively correct.

### Prior only Model with regularized Priors
Prior Exponent: `r round(mean(posterior.noise3$value),2)` [`r round(hdi_lower(posterior.noise3$value),2)` : `r round(hdi_upper(posterior.noise3$value),2)`].

@@

Qualitatively, predictions change again for different speaker - congruent (from above chance to below chance). This is somehow strange as the uniform prior prediction in this case would be chance. Why is the prediction pushed below chance? This doesn't really make sense.

4/8 predictions are qualitatively correct.

### RSA Model with regularized Priors
Prior Exponent: `r round(mean(posterior.noise2$value),2)` [`r round(hdi_lower(posterior.noise2$value),2)` : `r round(hdi_upper(posterior.noise2$value),2)`]

@@

6/8 predictions are qualitatively correct.

### Prior only Model with Noise and regularized Priors
Noise parameter: `r round(mean(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)`].

@@

6/8 predictions are qualitatively correct.

### RSA Model with Noise and regularized Priors
Mean noise parameter with 95% CrI: `r round(mean(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)`].

@@

8/8 predictions are qualitatively correct.

## Comparing models

Order of parameterized models makes sense when looking at the correlations and model predictions. However, the predictions from the non-parameterized models do not fit in. First, the Prior only model provided a better fit based on the previous

```{r model predictions log likelihood, include = FALSE}
c <- ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

@@

Log probabilities given the data for all models (except no prior model), computed via webppl.

```{r}
llh.plot%>%
  knitr::kable(digits = 2)
```

Log probabilities given the data for non-parameterized models based on binomial distribution (full model = RSA).

```{r}
comp_model%>%
  knitr::kable(digits = 2)
```
